Prediction of PIK3CA mutation with gene expression

### 2020-04-08 plosOne/plosOne.tex
pdf

@@

>>>>

PIK3CA prediction model performed better than RAS activation prediction
model in terms of AUROC. AUPR and the PIK3CA mutation rate
interpretation. {[}3{]}

@@

\leavevmode\hypertarget{ref-davis_2006_relationship_proc23rdintconfmachlearn}{}%
3. Davis J, Goadrich M. The relationship between Precision-Recall and
ROC curves. Proceedings of the 23rd international conference on Machine
learning. Pittsburgh, Pennsylvania, USA: Association for Computing
Machinery; 2006. pp. 233--240.
doi:\href{https://doi.org/10.1145/1143844.1143874}{10.1145/1143844.1143874}
